--- 
title: "TRABAJO DE CALIDAD DE AGUA RIMAC"
author: "Luis Edgar Gutierrez Saldaña" 
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---
# ACP

El análisis de componentes principales (ACP) consiste en expresar un conjunto de variables en un conjunto de combinaciones lineales de factores no correlacionados entre sí, estos factores dando cuenta una fracción cada vez más débil de la variabilidad de los datos.

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
